---
title: "TipsnTricks"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



## Compute canada workflow

### Interactive jobs

To test job submissions, etc.

```bash
salloc --time=1:0:0 --mem=3G --ntasks=1 --account=def-rainvilp 
module load python/3.10
module load  scipy-stack
source ENV/bin/activate
python ../main.py
```


### Git on```{language}

```

git config --global user.name "DylanSutterlin"
git config --global user.email "dylan.sutterlin-guindon@umontreal.ca"


git init 
git add .
git commit -m "first commit"
git remote add https://github.com/dylansutterlin/resting_state_hypnosis
git remote -v # to check that remote has been added

git checkout -b beluga # switch to beluga
git branch --show-current # just to print the branch if unsure

git push --set-upstream origin main # Asks username and password

# () to set up ssh
ssh-keygen -t ed25519 -C "dylan.sutterlin-guindon@umontreal.ca"
```

### BASH

```
cp [options] sourcefile targetfile

###
paths

/data/rainville/dylanSutterlin/Hypnosis_variables_20190114_pr_jc.xlsx

path = /data/rainville/HYPNOSIS_ASL_ANALYSIS/CBF_normalized

result = /data/rainville/dylanSutterlin/results/connectivity 

